\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-12 paper/paper.tex
add attack section, needs more

\subsection{Address utilization}

@@

-Fingerprinting Masked site vs Dark decoy application
-Active probing TLS connection
    -Block access unless from registering source IP
        -cite GFW taking over client IPs for active probing of old obfs
    -Verify knowledge of seed (but how to respond when verification fails?)
-ICMP

>>>>

\subsection{Address utilization}
% TODO:Can be better: story for v4, these are some problems, here's what it
% looks like in v6

@@

There are many attacks a censor might attempt to either prevent dark decoys from
being registered or used.

\paragraph{Blocking registration}
To make registration more difficult, censors could block TLS connections to all of the
limited decoys available in a deployment. Using TapDance's current deployment,
this would involve blocking over 1500 sites. We note that such an attack would
completely disable all existing Refraction Networking schemes, as none work
without being able to access legitimate decoys past the station. In dark decoys,
this would only block new registrations, and would not impact users that
previously registered. Furthermore, registrations could also occur over email,
or over lower-bandwidth covert channels, such as port (or even IP) knocking past
the station, that would be more difficult for the censor to block.
%Cirripede previously used a registration protocol that sent covert information via initial
%sequence numbers in arbitrary TCP connections, though we note this solution
%generally requires clients to have root access to their device to control the
%initial sequence numbers. Since most mobile users do not have such control, we
%suggest other methods be used instead.

\paragraph{Scanning masked sites}
The censor could also attempt to fingerprint the masked site and compare it to a
suspected dark decoy application. For instance, if a dark decoy IP responds as
pretending to be \texttt{example.com}, the censor could scan or probe real instances
of \texttt{example.com} on different ports and see how it responds. Then, the
censor can probe the dark decoy IP, and see if it responds similarly (e.g. with
the same set of open ports and payloads for certain kinds of probes). To defend
against this, we forward \emph{all} traffic destined to the dark decoy to the
masked site, including ports that are not relevant to the proxy application
(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
site. However, there may be differences in TCP/IP implementations, for instance,
how IP IDs are incremented, or how TCP timestamps are incremented (or supported
at all) that may be different from the mask site. To combat this, we can filter
mask sites by those that have identical TCP/IP stacks to ours, as we use a
common Linux implementation. We also note that this attack only applies when we
use the mask site as an application, and that Dark Decoys can support other
applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.

\paragraph{Website Fingerprinting}
Dark Decoy applications that mimic websites (e.g. mask sites) may be vulnerable
to website fingerprinting, where the censor observes that clients accessing
suspected dark decoy IPs are receiving payloads or packet timings that differ
from legitimate connections to the mask site. This attack is difficult for
censors to carry out because it has high uncertainty: even a small false
positive rate means blocking mostly legitimate connections (due to the base rate
of normal traffic), and false negatives could allow clients to retry until they
gain access. More importantly, unlike previous Refraction Networking protocols,
Dark Decoy applications are not limited to mimicking websites, and can support
any (or even a combination of) protocols.

%\paragraph{Probing Dark Decoys}
%-Active probing TLS connection
%    -Block access unless from registering source IP
%        -cite GFW taking over client IPs for active probing of old obfs
%    -Verify knowledge of seed (but how to respond when verification fails?)

\paragraph{ICMP}
Censors can use ping or traceroute utilities (via ICMP) to probe potential dark
decoys. Because there is (usually) no host at the dark decoy address, these
probes will timeout and produce no response. They might also produce
``Destination Unreachable'' responses from routers depending on how they are
configured.
% we scanned a random sample of v6 addresses and found...x%
% responded with ICMP dest unreach
Many legitimate hosts and routers do not respond to or forward ICMP packets, and
it is common for firewalls to block traceroutes from penetrating inside
networks. Thus, simply ignoring ICMP messages (or low TTL packets that might be
used by traceroute) may be a viable strategy. % We should evaluate this claim...
Alternatively, we could spoof responses to convince an adversary that a dark
decoy is part of a particular network. However, this strategy requires careful
consideration of what network makes sense for a mask site to be in. Also, the
censor may try to probe for addresses around the dark decoy (but still likely to
be in the same network), which must also be responded to.

%-Fingerprinting Masked site vs Dark decoy application
%-ICMP
